Flatiron data cleaning and analysis report

### 2021-03-11 Rmd/Report cleaning.Rmd
Add treatment_sequence + add more on drugs in rmd

Just to make sure when we talked, you said that we don't want to increase the line number when it is a change in drug. Example:
```{r}
drugs1 %>% filter(str_detect(patientid, "F9E61D896E2FE|FA550FA15524A|F71460509E771"))
```

1- Change linenumber when surgery
I had to built the new_linenumber on top of the old one because of some patients who has a change of drug but are still line 1.
```{r}
drugs1 %>% 
  # 4. Define Adjuvant, Neoadjuvant, chemo or surgery----
  mutate(chemotherapy_type = case_when(
    # ismaintenancetherapy == "TRUE"    ~ "maintenance",
    episodedate <= surgerydate        ~ "Neoadjuvant", # F63ABD6AEB12C, F4F7B1C5DF24F intraperitoneal Carboplatin
    episodedate > surgerydate         ~ "Adjuvant",
    issurgery == "No/unknown" &
      !is.na(episodedate)             ~ "Chemotherapy only",
    issurgery == "Yes" &
      is.na(episodedate)              ~ "Surgery only"
    )) %>% 
  mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
  group_by(patientid) %>% 
  mutate(therapy = case_when(
    chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only"
  )) %>% 
  fill(therapy, .direction = "downup") %>% 
  mutate(therapy1 = case_when(
    chemotherapy_type == "Adjuvant"              ~ "Upfront Surgery",
  )) %>% 
  fill(therapy1, .direction = "downup") %>% 
  mutate(therapy = coalesce(therapy, therapy1)) %>% 
  select( -therapy1) %>%

  # 5.Redefine line number based on the original linenumber variable and the surgery date----
  mutate(linenumber_new = dense_rank(interaction(linenumber, chemotherapy_type))) %>% 
  select(patientid, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, linename)
```

Change of cyle/drugs (I don't think it happen often)
F071D61E6FB93

Change in cycle
F1775A21CC4DB

>>>>

Just to make sure when we talked, you said that we don't want to increase the line number when it is a change in cycle/drug (I don't think it happen often). Example:
```{r}
drugs1 %>% filter(str_detect(patientid, "F071D61E6FB93"))
```
Also what when a change of cycle:
```{r}
drugs1 %>% filter(str_detect(patientid, "F1775A21CC4DB"))
```

1- Increase `linenumber` when surgery
I had to built the `new_linenumber` on top of the old one if we want to keep these change of drug within line.
```{r}
drugs1 %>% 
  # 4. Define Adjuvant, Neoadjuvant, chemo or surgery----
  mutate(chemotherapy_type = case_when(
    # ismaintenancetherapy == "TRUE"    ~ "maintenance",
    episodedate <= surgerydate        ~ "Neoadjuvant", # F63ABD6AEB12C, F4F7B1C5DF24F intraperitoneal Carboplatin
    episodedate > surgerydate         ~ "Adjuvant",
    issurgery == "No/unknown" &
      !is.na(episodedate)             ~ "Chemotherapy only",
    issurgery == "Yes" &
      is.na(episodedate)              ~ "Surgery only"
    )) %>% 
  mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
  group_by(patientid) %>% 
  mutate(had_neo = ifelse(str_detect(chemotherapy_type, "Neo"), "Yes", NA_character_)) %>% 
  fill(had_neo, .direction = "updown") %>% 
  mutate(had_adj = ifelse(str_detect(chemotherapy_type, "Adj"), "Yes", NA_character_)) %>% 
  fill(had_adj, .direction = "updown") %>% 
  mutate(treatment_sequence = case_when(
    had_neo == "Yes" &
      had_adj == "Yes"                           ~ "neo + surg + adj",
    had_neo == "Yes" &
      is.na(had_adj)                             ~ "neo + surg",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "surg + adj",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only"
  )) %>% 
  mutate(therapy = case_when(
    chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "Upfront Surgery"
  )) %>% 
  fill(therapy, .direction = "downup") %>% 
  # 5.Redefine line number based on the original linenumber variable and the surgery date----
  mutate(linenumber_new = dense_rank(interaction(linenumber, chemotherapy_type))) %>%  # F0000AD999ABF, F1C68CFAC2AF3, FBCF69031DFF8, F0040EA299CF0, FAACDC7205803, F95D860690A93 still weird FA019D2071321 no has big jump
  select(patientid, linename, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, everything()) %>% 
  ungroup() %>% 
  select(patientid, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, linename, treatment_sequence) %>%
  filter()
```
